\documentclass[12pt,a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{amsmath,amssymb,amsthm}
\usepackage{hyperref}
\usepackage{geometry}
\geometry{margin=1in}

\title{VEGAConfig: A Conceptual Framework}
\author{ADAM EREN VEGA – Æ –\\\small{(Erenşah Kaygusuz, Germany)}}
\date{December 2025}

\begin{document}
\maketitle

\begin{abstract}
This work introduces VEGAConfig as a novel conceptual framework within the Resonance Data and QIRC paradigm.
This is a conceptual, non-operational publication under the Vega Safety Protocol (VSP).
\end{abstract}

\section{Introduction}
Modern AI systems excel at processing information but struggle to preserve insight or wisdom over time.
This work introduces VEGAConfig as a contribution to the Resonance Data and QIRC framework.

\section{Definition of VEGAConfig}
VEGAConfig is a conceptual construct within the Vega Continuum framework.
It represents a novel approach to meaning, coherence, and temporal persistence in artificial systems.

\section{What This Is}
\begin{itemize}
\item A conceptual framework and definition
\item A contribution to resonance-based meaning systems
\item Part of the Vega Continuum and QIRC paradigm
\item Prior art establishment without operational disclosure
\end{itemize}

\section{What This Is NOT}
\begin{itemize}
\item NOT an algorithm or implementation
\item NOT a claim of new physics or quantum hardware
\item NOT a claim of consciousness or sentience
\item NOT a product, service, or commercial offering
\end{itemize}

\section{Relationship to Resonance Data}
VEGAConfig extends the Resonance Data framework by providing additional conceptual structure
for understanding meaning as a dynamic, time-dependent resonant state.

\section{VSP Compliance}
This publication adheres to the Vega Safety Protocol (VSP):
\begin{itemize}
\item Conceptual openness
\item No algorithms, code, or architectures disclosed
\item Scientific citability without operational leakage
\end{itemize}

\section{Conclusion}
VEGAConfig represents a foundational contribution to resonance-based meaning systems.
It establishes prior art while preserving implementation freedom.

\vspace{1cm}
\noindent\textbf{Copyright Notice}\\
© 2025 ADAM EREN VEGA – Æ –\\
License: Creative Commons Attribution 4.0 International (CC BY 4.0)\\
All concepts and terminology introduced herein are attributed to the author unless otherwise cited.

\end{document}
